The responses of \textit{\textit{Spinifex littoreus}} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2020-12-13 tex/interactcsesample.tex
update details

During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape. After measurements (in minutes generally), all the plants were buried again with the previous sand. When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label previously fixed on the stolons. Then all the samples were taken to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).

@@

\section{Conclusion}
The following conclusions may be made:
(1) All sand burial treatments had no significant impact on the growth of the height of ramets of \textit{S. littoreus}. However, the extension of its stolon was enhanced under intense sand burial (HI and CI) treatments by 24.56\% and 40.79\%, respectively.
(2) Sand burial increased the production of adventitious roots mainly in the base section of stolons, and germination of leaves on the apex of stolons, as adaptation strategies to long-last sand burials. 
(3) Based on highly adaptation to intense sand burial (even buried brought by typhoons), \textit{S. littoreus} can be one of the most protective and defensive species in the coastal ecological systems.

>>>>

During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape. After measurements (in minutes generally), all the plants were buried again with the previous sand. When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label on the stolons. Then all the samples were taken to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).

@@

\section{Conclusion}
The following conclusions may be made:

(1) All sand burial treatments had no significant impact on the growth of the height of ramets of \textit{S. littoreus}. However, the extension of its stolon was enhanced under intense sand burial (HI and CI) treatments by 24.56\% and 40.79\%, respectively.

(2) Sand burial increased the production of adventitious roots mainly in the base section of stolons, and germination of leaves on the apex of stolons, as adaptation strategies to long-last sand burials.

(3) Based on highly adaptation to intense sand burial (even buried brought by typhoons), \textit{S. littoreus} can be one of the most protective and defensive species in the coastal ecological systems.
